Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-03-14 paperDistance/paper.tex
placeholders for assumptions and pedagogy

@@

\begin{itemize}
\item The photometric uncertainties in the J band are small compared with the uncertainties in the parallax
\item Our empirical bayes approach is ok as long as we only infer information about the data contained within the prior
\item the uncertainties are gaussian
\item most stars lie where we expect them to on the CMD
\item number of gaussians that's efficient? or do x-validation
\item can't think
\end{itemize}

>>>>

\section{Why does this work?}

LA+DWH: Do we we want to put a pedagogical section in right here?

Hogg would propose a straight-line fit (possibly with intrinsic
width); showing that it can be used to de-noise noisy y-data.

@@

\begin{itemize}
\item Some kind of stationarity assumption.
\item Our empirical bayes approach is ok---that is, our numbers are large enough.
\item The photometric uncertainties in the J band are small compared with the uncertainties in the parallax; the uncertainties are gaussian
\item number of gaussians
\item no use of physical models, baby!
\end{itemize}
